Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
a little bit more fooling with space
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51106 72bbbca6-d526-0410-a7d9-f06f51895060
some more minor stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51107 72bbbca6-d526-0410-a7d9-f06f51895060

\caption{Number of stems and coverage of a corpus over time for the Kumyk transducer. Time is measured in days 
starting from the 2nd October 2013. The graph shows that to reach 80\% coverage took
around a week, and to reach 90\% took another week.}
\label{fig:kumcov}
\end{figure}

@@

In Kazakh, ‹е› is a front diphthong (e.g., ‹елдің› `country-\tags{gen}'), but in e.g., family names with Russian morphology, it harmonises as a back vowel (e.g., ‹Назарбаевтың› `Nazarbayev-\gmk{gen}').

@@

%FIXME: footnote with urls
This list of surface forms was then analysed with the most recent version of the analyser, and each analysis was checked.  Where an analysis was erroneous, it was removed; where an analysis was missing, it was added.  This process gave us a `gold standard' morphologically analysed word list of 1,000 (Kazakh and Tatar) and 500 (Kumyk) surface forms with their analyses.  The list is publically available for each language.%\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/eval/ref.1000.txt}}

>>>>

\caption{Number of stems and coverage of a corpus over time for the Kumyk transducer. Time is measured in days 
starting from the 2nd October 2013. The graph shows that to reach 80\% coverage took
around a week, and to reach 90\% took another week.}
\label{fig:kumcov}
\vspace{-0.5em}
\end{figure}

@@

In Kazakh, ‹е› is a front diphthong (e.g., ‹елдің› `country-\gmk{gen}'), but in e.g., family names with Russian morphology, it harmonises as a back vowel (e.g., ‹Назарбаевтың› `Nazarbayev-\gmk{gen}').

@@

%FIXME: footnote with urls
This list of surface forms was then analysed with the most recent version of the analyser, and each analysis was checked.  Where an analysis was erroneous, it was removed; where an analysis was missing, it was added.  This process gave us a `gold standard' morphologically analysed word list of 1,000 forms for Kazakh and Tatar and 500 forms for Kumyk, along with their analyses.  The list is publically available for each language in Apertium's svn repository.%\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/eval/ref.1000.txt}}
